Reanalysis Step 2: Multiple Imputation

### 2025-08-19 reanalysis-2-multiple_imputation.qmd
final mi

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 5 iterations (fast)
# final = 30 imputations, 20 iterations (slow but thorough)
analysis_mode <- "test"  # Change to "final" for production run

>>>>

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 5 iterations (fast)
# final = 30 imputations, 20 iterations (slow but thorough)
analysis_mode <- "final"  # Change to "final" for production run
